---
title: "Submission Sample"
author: "Samuel Chan"
date: "9/15/2018"
output:
  html_document: default
  pdf_document: default
  word_document: default
---
## R Markdown
First, we'll read in some data to work with. The data are downloaded from the [Finhacks](http://finhacks.id) website, and are available to all participants.

```{r}
bca <- read.csv("data_input/bca_wikipedia.csv")
str(bca)
```

```{r}
# here I'm converting the date
bca$date <- as.Date(bca$date)
plot(x=bca$date, 
     y=bca$views, 
     type="l",
     main="BCA Wikipedia views since 2015",
     col="hotpink2"
     )
```

# Exploratory Analysis
This part of the report describes the action and strategy I'm taking. 
- Clean the data  
- Pre-processing  
- Inspect the trend  
- Feature Engineering

Because Sam said feature engineering is paramount to building a good machine learning model.

First step, let's clean the data up by converting `date` to a Date object:
```{r}
bca_n <- bca[,8:9]
bca_n$date <- as.Date(bca_n$date)
range(bca_n$date)
```


Between weekdays and weekend, which is better for business?
```{r}
bca_n$month <- as.factor(months(bca_n$date))
bca_n$dayofweek <- as.factor(weekdays(bca_n$date))
bca_n$isWeekend <- as.factor(ifelse(bca_n$dayofweek == "Saturday" | bca_n$dayofweek == "Sunday", "Weekend", "Weekday"))
tail(bca_n)
```

Simple visualization to see if there's a difference in views across different days of the week:
```{r}
plot(x=bca_n$dayofweek, y=bca_n$views, main="ATM withdrawals across different days of month")
```


```{r}
xtabs(views ~ dayofweek + month, bca_n)
```

## Machine Learning Model
This section of the report describes my model construction, and the choice of algorithm.





